\begin{thebibliography}{99}

  \bibitem{bsynth}

  Daniel R. Mitchell,

  \emph{BasicSynth: Creating a Music Synthesizer in Software}.

  Publisher: Author.

  1st Edition,

  2008.

  \bibitem{dspguide}

  Steven W. Smith,

  \emph{The Scientist and Engineer's Guide to Digital Signal Processing}.

  California Technical Publishing,

  San Diego, California,

  2nd Edition,

  1999.

  \bibitem{oxdic}

  Ed: Catherine Soanes and Angus Stevenson,

  \emph{Oxford Dictionary of English}.

  Oxford University Press,

  Oxford,

  2003.
  
  \bibitem{filtercoef}
  
  Robert Bristow-Johnson,
  
  \emph{Cookbook formulae for audio EQ biquad filter coefficients}.
  
  \url{http://www.musicdsp.org/files/Audio-EQ-Cookbook.txt}
  
  Accessed: 4 January 2015.

  \bibitem{musco}

  Phil Burk, Larry Polansky, Douglas Repetto, Mary Roberts and Dan Rockmore,

  \emph{Music and Computers: A Historical and Theoretical Approach}.

  2011

  \url{http://music.columbia.edu/cmc/MusicAndComputers/}

  Accessed: 22 December 2014.

  \bibitem{sosfm1}

  Gordon Reid,

  \emph{Synth Secrets, Part 12: An Introduction To Frequency Modulation}.

  \url{http://www.soundonsound.com/sos/apr00/articles/synthsecrets.htm}

  Accessed: 30 December 2014.

  \bibitem{sosfm2}

  Gordon Reid,

  \emph{Synth Secrets, Part 13: More On Frequency Modulation}.

  \url{http://www.soundonsound.com/sos/may00/articles/synth.htm}

  Accessed: 30 December 2014.

  \bibitem{sfufm}

  \emph{Tutorial for Frequency Modulation Synthesis}.

  \url{http://www.sfu.ca/~truax/fmtut.html}

  Accessed: 30 December 2014.

  \bibitem{samplerates}

  Justin Colletti,

  \emph{The Science of Sample Rates (When Higher Is Better —-- And When It Isn't)}.

  2013.\\
  \url{http://www.trustmeimascientist.com/2013/02/04/the-science-of-sample-rates-when-higher-is-better-and-when-it-isnt/}

  Accessed: 17 December 2014.

  \bibitem{hearing}

  John D. Cutnell and Kenneth W. Johnson,

  \emph{Physics}.

  Wiley,

  New York,

  4th Edition,

  1998.

  \bibitem{wave}

  Scott Wilson,

  \emph{WAVE PCM soundfile format}.

  2003.

  \url{https://ccrma.stanford.edu/courses/422/projects/WaveFormat/}

  Accessed: 2 January 2015.

  \bibitem{midi}

  Dominique Vandenneucker,

  \emph{MIDI Tutorial}.

  2012.

  \url{http://www.cs.cmu.edu/~music/cmsip/readings/MIDI%20tutorial%20for%20programmers.html}

  Accessed: 2 January 2015.

  \bibitem{fmlevel}

  User \emph{JCPedroza},

  \emph{What is the level of frequency modulation of many synthesizers?}.

  \url{http://sound.stackexchange.com/questions/31709/what-is-the-level-of-frequency-modulation-of-many-synthesizers}

  Accessed: 3 January 2015.
  
  \bibitem{dx7}
  
	Electronic Music Wiki,
  
	\emph{DX7}.
  
    \url{http://electronicmusic.wikia.com/wiki/DX7}
    
    Accessed: 4 January 2015.
    
   \bibitem{malstrom}
    
	Propellerhead,
	
	\emph{Malstr{\"o}m Graintable Synthesizer}.
	
	\url{https://www.propellerheads.se/products/reason/instruments/malstrom/}	
	
	Accessed: 4 January 2015.

\end{thebibliography}
